Robustly decorrelating errors with mixed quantum gates

### 2020-01-13 decorrelation/arxiv/mixed_unitaries.tex
adding in first version submitted to arxiv, and document now has typos fixed by earl

Randomized protocols have a long history of outperforming their deterministic counterparts\cite{Viola2005, Santos2006}. In circuit models, Pauli Frame Randomization \cite{Wallman2016, 1803.01818} has been shown to reduce coherent errors by introducing randomness in a pre-compilation step. While Pauli Frame Randomization shares the some favorable properties with MQGs, we will see that MQGs additionally admit a hardware-efficient implementation and numerous useful modifications when they are posed as a numerical optimization problem.

>>>>

Randomized protocols have a long history of outperforming their deterministic counterparts\cite{Viola2005, Santos2006}. In circuit models, Pauli Frame Randomization \cite{Wallman2016, 1803.01818, dahlen2018experimental} has been shown to reduce coherent errors by introducing randomness in a pre-compilation step. While Pauli Frame Randomization shares the some favorable properties with MQGs, we will see that MQGs additionally admit a hardware-efficient implementation and numerous useful modifications when they are posed as a numerical optimization problem.
